Hydras \& Co.: Formalized mathematics in Coq\\ for inspiration and entertainment

### 2022-06-02 doc/JFLA2022/Slides/Slides.tex
small changes to JFLA slides

\begin{scope}[yshift=-5cm,xshift=4cm]
\node[rectangle, draw=black,fill=red!80,minimum height=0.5cm,minimum width=1.5cm] (book) { \Hydras};  
\end{scope}

\draw[lookcolor,->,dotted] (acl2.south) -- (cantor.north) ;
\draw[lookcolor,->,dashed] (additions.south west) -- (chains.north) ;
\draw[lookcolor,->,dashed] (goedel) -- (goedelcc) ;
\draw[lookcolor,->,dashed] (goedel) -- (hydras.north) ;
\draw[lookcolor,->,dashed] (cantor) -- (hydras.north east) ;
\draw[lookcolor,->,dashed] (cantor.south) -- (gaia.north west) ;
\draw[lookcolor,->,dashed] (pock) -- (pockcc) ;
\draw[lookcolor,->,dashed] ([xshift=2.1cm]cats) -- (gaia) ;

@@

\draw[->] (mathcomp) -- (gaia) ;
\draw[->] (mathcomp) -- (chains) ;
\draw[->] (paramcoq.south) -- (chains) ;
\draw[->] (pockcc) -- (goedelcc) ;
\draw[dotted, ->] (prooftheory) -- (hydras);
\draw[dotted, ->] (settheory) -- (cats);
\draw[dotted, ->] (prooftheory) -- (goedel);
\draw[dotted, ->] (algo) -- (additions);
\draw[->, red] (alectryon) -- (book) ;
\draw[->, red] (chains) -- (book) ;
\draw[->, red] (gaiahydras) -- (book) ;
\draw[->, red] (hydras.south) -- (book) ;

\end{tikzpicture}
}
% \caption{Genealogy and dependencies for \Hydras.}
%   \label{fig:genealogy}
% \end{figure}
\end{frame}

@@

\begin{frame}
  \frametitle{Compatibility with Gaia}
  \begin{block}{From \Hydras to \gaia}
    {\footnotesize
      \inputsnippets{./canonDef}
      \inputsnippets{./gcanonLimitOf}}
  \end{block}
  \begin{block}{}
    We experiment also the other direction (importing \texttt{ssete9} lemmas to \Hydras).
  \end{block}
\end{frame}

>>>>

\begin{scope}[yshift=-5cm,xshift=4cm]
  \node[rectangle, draw=black,fill=red!60,minimum height=0.5cm,minimum width=1.5cm] (book) {hydras.pdf};
    \node[rectangle, draw=black,minimum height=0.5cm,minimum width=1.5cm, left of=book, node distance=6cm] (latex) {hydras.tex};
\end{scope}

\draw[lookcolor,->,dotted] (acl2.south) -- (cantor.north) ;
\draw[lookcolor,->,dashed] (additions.south west) -- (chains.north) ;
\draw[lookcolor,->,dashed] (goedel) -- (goedelcc) ;
\draw[lookcolor,->,dashed] (goedel) -- (hydras.north) ;
\draw[lookcolor,->,dashed] (cantor) -- (hydras.north) ;
\draw[lookcolor,->,dashed] (cantor.south) -- (gaia.north west) ;
\draw[lookcolor,->,dashed] (pock) -- (pockcc) ;
\draw[lookcolor,->,dashed] ([xshift=2.1cm]cats) -- (gaia) ;

@@

\draw[->] (mathcomp) -- (gaia) ;
\draw[->] (mathcomp) -- (chains) ;
\draw[->] (paramcoq.south) -- (chains) ;
\draw[->] (pockcc) -- (goedelcc) ;
\draw[dotted, ->] (prooftheory) -- (hydras);
\draw[dotted, ->] (settheory) -- (cats);
\draw[dotted, ->] (prooftheory) -- (goedel);
\draw[dotted, ->] (algo) -- (additions);
\draw[->, red] (alectryon) -- (book) ;
\draw[->, red] (chains) -- (book) ;
\draw[->, red] (gaiahydras) -- (book) ;
\draw[->, red] (hydras.south) -- (book) ;
\draw[->, red] (latex) -- (book) ;
\end{tikzpicture}
}
% \caption{Genealogy and dependencies for \Hydras.}
%   \label{fig:genealogy}
% \end{figure}
\end{frame}

@@

\begin{frame}
  \frametitle{Compatibility with Gaia}
  \begin{block}{From \Hydras to \gaia}
    {\footnotesize
      \inputsnippets{./canonDef}
      \inputsnippets{./gcanonSLE}
      \inputsnippets{./gcanonLimitOf}}

  \end{block}
  \begin{block}{}
    We experiment also the other direction (importing \texttt{ssete9} lemmas to \Hydras).
  \end{block}
\end{frame}
